Intentional release of native species undermines ecological stability

### 2022-03-14 rmd/manuscript.Rmd
edit: double-blind

We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Genki Sahashi and Masato Yamamichi for helpful discussion on this manuscript.

@@

AT conceived the project. AT, HU and BN assembled data for empirical analysis. AT analyzed data with inputs from HU, MS, and BN. AT wrote the first draft and HU, MS, and BN significantly contributed to the final version of the manuscript.

@@

Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.

>>>>

Blinded for double-blind review

@@

Blinded for double-blind review

@@

Data and codes will be made available upon the acceptance of the manuscript.
